The Machines are Among Us

### 2020-12-03 paper/main.tex
finalize paper, clean up repository

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{Machines are Among Us}

\author{Zach Minot\\
Georgia Institute of Technology\\
2nd Year Undergraduate, CS\\
{\tt\small zjminot@gatech.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Charles Gunn\\
Georgia Institute of Technology\\
2nd Year Undergraduate, CS \& Math\\
{\tt\small cgunn30@gatech.edu}
}

@@

%%%%%%%%% ABSTRACTcommunicate
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

>>>>

\usepackage[breaklinks=true,bookmarks=false]{hyperref}

@@

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\setcounter{page}{1}
\begin{document}

%%%%%%%%% TITLE
\title{The Machines are Among Us}

\author{Zach Minot\\
Georgia Institute of Technology\\
2nd Year Undergraduate, CS\\
{\tt\small zjminot@gatech.edu}
\and
Charles Gunn\\
Georgia Institute of Technology\\
2nd Year Undergraduate, CS \& Math\\
{\tt\small cgunn30@gatech.edu}
}

@@

%%%%%%%%% ABSTRACTcommunicate
\begin{abstract}
   In this paper, we explore techniques for training sets of deep adversarial neural networks
   to communicate with each other. In order to investigate this, we took inspiration
   from the game Among Us to develop a scenario in which multiple agents could
   communicate and compete with each other. By running a variety of tests spanning
   many conditions for the sets of networks, we learn that communication between
   these networks is volatile, and that often simply the process of developing a
   common ``language'' of communication between multiple networks poses
   challenges.
\end{abstract}
